|

### 2021-08-21 appendix/appendix.Rmd
appendix structure

---
title: |
       | Supplementary Materials for "Legislature Size and Welfare: Evidence from Brazil"
author:
  - Gabriel Cepaluni[^gabriel]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.

[^gabriel]: Associate Professor, Department of International Relations, São Paulo State University, <gabi.cepal@gmail.com>.

\appendix
\addtocounter{section}{2}

@@

## A Model of Legislature Size and Service Provision

### Primitives of the Model

Consider an strategic interaction between a mayor ($M$) and $N \geq 3$ city councilors, indexed in $i \in \{1, 2, \cdots, N \}$. The mayor is the head of the local executive branch, and has the prerogative of proposing a vector of policies, that is voted by the city councilors. Policy proposals are a combination of public goods provision $g$, rents for the mayor $r$, and a vector of transfer for city councilors \textbf{x}.

The city council votes the mayor's proposal and if they accept it, it is implemented. Otherwise, a reversal policy takes place. Reversal policy in this context means that the mayor's proposal failed to secure majority of council votes. The decision process leaves the mayor's office, and either immediately stops or it is transferred to the council. The types of reversal policies are crucial for our argument, as it changes the relative strength of the council in their bargaining with the mayor. We investigate three types of reversal policies: a \textit{non-partisan} reversal mechanism, where city councilors have no partisan affiliation; a \textit{partisan} reversal mechanism, where the council is divided in supporters and non-supporters of the mayor; and finally a \textit{hybrid} reversal mechanism, that combines partisan with non-partisan features. In the main paper, we focus on the hybrid model, as it is the more realistic scenario. Despite that, comparing the partisan and non-partisan reversal mechanisms illustrate clearly our argument that the partisan a mechanism is what drives our results.

To govern, the mayor has to convince at least half of the city councilors to support her policy proposals. Similar to \citet{buenodemesquita2005logic}, we assume that the selectorate, i.e. the individuals that have a say in the mayor's policy proposals, are the $N$ city councilors. The winning coalition, which is the minimum number of members that have to be convinced to implement the policy, is equal to half of the selectorate $N/2$. City councilors are moved by policy concerns $p$ and transfers received from the mayor or the councilor recognized as the proposer \textbf{x}. We leave the definition of these transfers open, as this facilitates the relation with several instruments that mayors can use to pressure city councilors. To illustrate, examples of transfers are granting electoral favors, spending in areas that the councilor has political or personal interests, granting portfolio and public jobs within the municipal bureaucracy, or even campaign contributions and bribes. The use of transfers to affect the councilors' choices and generate a governing cost of $C_G$. The governing costs vary with the reversal mechanism and the legislature size.

Finally, after paying the costs of govern, the mayor proposes a level of public goods provision ($g$) and rents ($r$). Public goods provision help the mayor to get reelected. Rents are for direct mayor's consumption, and does not contribute to the mayor's electoral success. This makes the mayor's expected utility a sum of the gains from rents and the benefits from reelection. Both the utilities from rents $u(.)$ and the probability of reelection $\pi(.)$ are concave functions, meaning that more rents or public goods increase the utility at a decreasing rate.\footnote{In technical terms, $u'>0$ and $\pi'>0$; and $u''<0$ and $\pi''<0$.} The probability of reelection is multiplied by the benefit from holding office $B_M > 0$. This benefit captures the tangible and intangible gains that the mayor perceives from holding the public office. We assume that the benefits are high enough to rule out an equilibrium with only rents and transfers, which is equivalent to say that mayors have a strong preference to be reelected. If the mayor's policy proposal is approved, then the expected utility for the mayor is:

\[
\mathbb{E}U(r, g) \ = \ u(r) + B_M\pi(g)
\]

The policy choices of the mayor are subject to the municipal budget constraint. The municipality has $R > 0$ resources, and cannot run debts, meaning that the budget has to be balanced. We also assume that there are enough resources for the mayor to govern.

Let $C_G$ be the costs of govern. The budget balance constraint requires the offers that the mayor makes to the city councilors satisfy the following inequality:

\[
r + g + C_G \ \leq \ R
\]

The expected utility for the city councilors depend on the reversal policy. As discussed, we explore three different mechanisms. First, in \textit{non-partisan} reversal mechanism, when the council rejects the mayor's proposal, a reversal stage starts with resources diminish by a factor of $\delta \in (0,1)$ and the selection of one councilor randomly. The randomly selected councilor becomes the new proposer. If her proposal is accepted, it is implemented. If it is rejected, the budget shrinks again by a factor $\delta$, and another city councilor is recognized to make the proposal. The process repeats, until one proposal is finally accepted.

In the second reversal mode, the \textit{partisan} reversal mechanism, we assume that each councilor has a party affiliation. Party affiliations are mutually exclusive (a councilor cannot belong to two parties at once). If a city councilor is affiliated to a party aligned with the mayor, we say that she belongs to the government coalition $G \subset \{1, 2, \cdots, N \}$. Otherwise, the city councilor belongs to the opposition $O  = \{1, 2, \cdots, N \} \setminus G$. The mayor's policy generate a political value of $p > 0$ for the councilors, and whether it adds or subtracts from the councilor's utility depends of the party affiliation of the councilor. If the mayor's proposal is rejected, a city councilor aligned with the mayor, that would receive $p$ from the policy, now receives zero. On the other hand, a city councilor that belongs to the opposition would receive $-p$ from the mayor's policy, and now receives zero. Although these assumptions are strong, they capture the underlying political dynamics of partisanship: the political preferences in terms of public goods provision are shared by councilors aligned with the mayor. Voting against the mayor's proposals would represent to defy the partisan label.

Lastly, in the \textit{hybrid} reversal mechanism, we combine partisanship with legislature bargaining costs. Councilors in this mechanism receive a partisan utility from the mayor's policy, but if they reject the policy, a reversal policy similar to the non-partisan reversal mechanism takes place. In the mayor's proposal stage, city councilors that belong to the mayor's coalition receive a gain of $p > 0$ when the mayor's policy is implemented. Opposition members, on the other hand, receive $-p$ when the mayor's proposal is implemented. If the mayor's proposal is rejected, as the city council does not control the Executive when the two branches are separated, no public goods are provided ($p=0$). Moreover, in equilibrium, we assume that city councilors would prefer to receive transfers instead of providing public goods. This aligns with the empirical evidence in most developing economies.

The timeline of the game is as follows:

\begin{enumerate}
  \item The mayor learns how many government $|G|$ and opposition $|O|$ legislators were elected.
  \item The mayor proposes a policy vector $(r, g, x)_M$.
  \item The city council votes the proposal.
  \begin{itemize}
    \item If the council accepts, the policy is implemented and the game ends. 
    \item Otherwise, the reversal policy is implemented.
  \end{itemize}
  \item (Reversal Policy) Depends on which mechanism, we have three different reversal policies. The details are in the following sections.
\end{enumerate}

The solution concept we use in this model is the Sub-game Perfect Nash Equilibrium. A Sub-game Perfect Nash Equilibrium requires that the strategies played are a Nash Equilibrium in each of the subgames of the game. The solution is found using backward induction. In the model with infinitely repeated proposals, we extend the equilibrium concept to require that the equilibrium is Stationary. A Stationary Sub-game Perfect Equilibrium requires that, at each given point of the game, if a politician accepts an offer at time $k+1$, she should accept the same offer at time $k$. Stationarity gives us an objective of finding an offer that would be accepted at any stage in the game. Applying this reasoning, we can find a sequence of offers for each point $k$ in time. For the mayor, the optimal offer is at $k=0$, and this represents a no delay in policy implementation.

\begin{definition}
The equilibrium for the game consists in a sequence of strategic policy vectors $(g^*, r^*, x^*)_k$, indexed in $k \in \{0, 1, \cdots, \infty\}$, such that, at every stage of the game, the mayor and the councilors have no profitable deviations from the equilibrium.
\end{definition}

Moreover, we assume that the players play no dominated strategies, even when there is less than sufficient support for implementing the policy.

### The Mayor's Decision Stage

Solving the game by backward induction requires us to start with the councilor's strategies. However, for exposure convenience, assume at this point that we solved the the game for the councilors, and found the equilibrium cost of govern $C_G(N)$ when there are $N$ city councilors. In the next section, we define $C_G(N)$ for each of the mechanisms using backward induction, and the definitions are well-behaved. In this section, we use this assumption to simplify the exposition.

We now derive the optimal rents ($r$) and public goods provision ($g$) proposed by the mayor. The mayor benefits from public goods provision, as it increases the chances of her reelection. However, she prefers to contribute as minimum as necessary for the public goods, and extract the remaining resources as political rents. The mayor's objective is to maximize her expected utility, subject to the municipal budget constraint.

\[
\begin{aligned}
\max_{r, g} \quad & u(r) + B_M\pi(g)\\
\textrm{s.t.} \quad & r + g + C_G(N) \leq R
\end{aligned}
\]

In equilibrium the budget binds, and the public goods provision maximizes:

\[
\max_{g} \{ u(R - g - C_G(N)) + B_M\pi(g) \}
\]

The first order condition for an optimal public goods provision makes the marginal benefits to increase rents, in this case, marginal costs of providing the public goods, equals to the marginal benefits of reelection:

\[
u'(R - g - C_G(N)) = B_M\pi'(g)
\]

This is sufficient for the equilibrium, as the second order condition reassures the concavity of the mayor's expected utility: $u''(R - g^* - C_G(N)) + B_M\pi''(g^*) < 0$.

\begin{proposition}
The provision of public goods increase with legislature size when the costs of govern decrease with legislature size.
\end{proposition}

\begin{proof}
To prove this result we need to show that the mayor's expected utility satisfy the increasing differences in $g$ and $N$. This would mean that when increasing the size of the council, the optimal solution $g^*$ would also increase. However, as $N$ increases discretely, we cannot take a the cross-partial derivative on $N$ or even use the implicit function theorem. Instead, we use monotone comparative statics to derive these results \citep{milgrom1994monotone}.

The mayor's expected utility satisfy the increasing differences in $g$ and $N$ when, for $g > g'$ and $N+1 > N$,\footnote{Moreover, the requirement that the decision and type space is a complete lattice, is satisfied for $\mathbb{R} \times \mathbb{N}$.} we have:

\[
\mathbb{E}\text{U}(g, N+1) - \mathbb{E}\text{U}(g', N+1) \geq \mathbb{E}\text{U}(g, N) - \mathbb{E}\text{U}(g', N)
\]

After substituting, we have:

\[
u(R - g - C_G(N+1)) + B_M\pi(g) - u(R - g' - C_G(N+1)) - B_M\pi(g') \geq 
u(R - g - C_G(N)) + B_M\pi(g) - u(R - g' - C_G(N)) - B_M\pi(g')
\]

Which is equal to:

\[
u(R - g - C_G(N+1)) - u(R - g' - C_G(N+1)) \geq 
u(R - g - C_G(N)) - u(R - g' - C_G(N))
\]

Multiplying both sides by $\dfrac{1}{g - g'}$ and taking the limit when $g \rightarrow g'$, we have:

\[
u'(R - g - C_G(N+1)) \geq 
u'(R - g - C_G(N))
\]

It is now clear to see that the function satisfies the increasing differences in $g$ and $N$ when the governing costs of a $N+1$-sized city council is lower than the governing costs of a $N$-sized city council:

\[
C_G(N+1) \leq C_G(N)
\]

@@

This provides us our first empirical hypothesis to test: \textit{if the governing costs decrease when the legislature increases, then the public goods provision increase when the legislature size increase}.

At this stage, we need to solve for existence of these governing costs. Below we show that this proposition is true for the *partisan* and *hybrid* mechanisms, but it is not true for the *non-partisan* mechanism.

### Non-Partisan Reversal Mechanism

In the \textit{non-partisan reversal} mechanism, we assume that when the council rejects the mayor's office, a reversal stage starts with the selection of one councilor randomly. To find the stationary sub-game perfect Nash equilibrium, suppose that there were $k-1$ rejections, and we are at the $k$-th stage in the game. A councilor accepts the proposer's offer if, and only if, to accept the offer at $k$ is better than to wait until the next stage $k+1$. If the offer is $x_i$, then:

\[
x_i \geq \dfrac{1}{N}\left[ \delta^{k+1}R - \dfrac{N}{2}x_i \right] + \left( 1 - \dfrac{1}{N} \right)\left[\dfrac{1}{2} x_i \right]
\]

In the left-hand side, we place the offer. In the right-hand side, there are two components. The first is the amount that the councilor $i$ gets when she is the proposer. It is equal to the chance that she is recognized as the proposer times the budget in the next round minus the offers that she has to make to convince half of the councilors. The second part is the gains if when the councilor happens to reject the current received offer, but still receives an offer in the following round. It is equal to the chance that she is not recognized as the proposer times the chance that she receives a transfer times the amount of the transfer. Note that the offer the councilor makes as the proposer is the same as the offer that she wants to receive. This because the city councilors are exchangeable, and the solution is symmetric for all councilors receiving an offer (this means that, without loss of generality, we could have dropped the $i$ in the solution). After some algebra, the offer $x_i$ has to be greater than or equal to:

\[
x_i \geq \dfrac{2 \delta^{k+1}R}{2N + 1} \equiv \underline{x}(k, N)
\]

The proposer always offer the minimum required to get the proposal approved. In the case, the offer at any given stage $k$ is going to be equal to $\underline{x}(k, N)$.

Proceeding backwards, at the mayor's proposal stage $k=0$ and the mayor is going to offer $\underline{x}(0, N) = \dfrac{2 \delta R}{2N + 1}$ to half of the councilors. In this context, the governing costs for the mayor are:

\[
C_G(N) \ = \ \dfrac{N}{2}\left[\dfrac{2 \delta R }{2N + 1}\right] \ = \ \dfrac{\delta R N}{2N + 1}
\]

\begin{proposition}
In the \textit{non-partisan reversal} mechanism, the governing costs always increase when the size of the legislature increases.
\end{proposition}

>>>>

---
title: |
       | Supplementary Materials for "Electoral Systems, Competition, and Incentives for Corruption"
author:
  - Umberto Mignozzetti[^umberto]
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.

\appendix

@@

# Formal Model
\label{app:specs}

Consider three sets of players: a set of incumbents $ I \ = \ \{ I_1, \ \cdots, \ I_K \}$, a set of challengers $C \ = \ \{ C_1, \ \cdots, \ C_L \}$, and a continuum of $V$ voters.

Each incumbent has a budget of $A$ units, that has to be invested in public goods. The level of expenditure necessary to provide the goods is a random variable $\eta \in [0,A]$, where $\eta \sim f(\eta)$, and $f$ is a weakly increasing PDF function with CDF $F$. If the public goods are successfully provided, we say that the policy result is good ($\psi = G$). Otherwise, we say the policy result is bad ($\psi = B$).

Let $\e$ be the vector of expenditures enacted by the incumbents. The public goods are provided whenever $K \cdot \eta \leq \sum_i e_i$, where $K$ represents number of incumbents. I assume that all incumbents observe the true $\eta$, and it is common-knowledge among them.

After choosing the expenditures, the public goods provision is realized and is common knowledge to all players. Now the campaign stage starts. Challengers face no running costs, and although they do not observe $\eta$, they know $\e$ and $\psi$.\footnote{This assumption does not change the game because an entry cost would only shift the equilibrium, preserving its qualitative characteristics.}

Upon observing $\e$ and $\psi$, challengers update their beliefs about $\eta$, and decide simultaneously weather to use negative campaign against the incumbents, paying a cost of $c \in \mathbb{R}_{+}$ whenever they use their full resources to expose a corrupt incumbent. After their decisions, the result is a vector $\dd \in \{0,1\}^{K}$ of sucessfully exposed corrupt incumbents, for each incumbent $i$ in $\{1, \cdots, K\}$. The probability that challenger $j$ investigating $i$ credibly communicate the $i$'s true corruption engagement to the voter is $\lambda: [0,A] \rightarrow [0,1]$. I assume $\lambda(0) = 0$ and $\lambda^{'} > 0$. Therefore, the probability of being credibly exposed depends on the distance between the optimal expenditure and the amount spend by the incumbent.

Finally, the voters have to decide whether to retain or dismiss the incumbents, upon observing $\psi$ and $\dd$. Their choices are summarized in a vector $\bups \in \{0,1\}^{K+L}$, where $1$ means that the politician is elected (or reelected, in case of an incumbent) and $0$, meaning not elected. We have that $\sum_i \upsilon_i = K$, and when the voter is asked to decide, she cannot change the results of $\psi$ and $\dd$. The voters' decisions are always sequentially rational. Therefore, I impose that they behave optimally by dismissing an incumbent $j$ that were credibly related with corruption, or all incumbents, when $\psi=B$.

The time-line of the game is as follows:

\begin{enumerate}
 \item The nature draws $\eta$;
 \item Each incumbent observes $\eta$ and chooses, simultaneously, $\e$;
 \item $\psi$ is realized. Challengers choose, also simultaneously, whether to invest resources to expose corrupt incumbents;
 \item The vector of successfully exposed incumbents $\dd$ are realized. The voter chooses $\bups(\psi, \ \dd)$ and the game ends.
\end{enumerate}

An incumbent $i$'s strategy is defined as:

\[
\varepsilon_i:[0,A] \rightarrow [0,A] 
\]

And the challenger $j$'s strategy is defined as:

\[
\bvphi_j:\{G, \ B \} \times [0,A]^K \rightarrow [0,1]^K
\]

Representing the amount of time invested by each challenger $j \in \{1, \cdots , L \}$ to expose an incumbent $i$. Notice that $\bvphi_j$ is a vector of size $K$, where each component is the probability of exposing one of the incumbents. For the representative voter we have:

\[
\bups:\{G, \ B \} \times \{0, \ 1 \}^{K} \rightarrow \{0, \ 1 \}^{K+L}
\]

That represents the decision to retain or dismiss each politician, with their replacement. The expected utilities for each player are, for the incumbents:

\[
U_i (\varepsilon_i; \ \eta, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) \ = \ u(\varepsilon_i - \eta) + B \ \Prob (\upsilon_i = 1 \ | \ \psi, \dd) 
\]

Where $B$ is the reward for staying in office (assumed the same for every player) and $\Prob (\upsilon_i = 1 \ | \ \psi, \dd)$ is the probability of being retained, given $\psi$ and the exposure profile $\dd$. For the challenger $j$:

\[
U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}) \ = \ B \int_{0}^A \Prob (\upsilon_j = 1 \ | \ \eta, \bveps^{*}, \bvphi^{*})\mu(\eta|\bveps^{*}) d\mu(\eta) - c \sum_{i=1}^K \varphi_{ij}(\psi, \bveps^{*})
\]

With $c > 0$ being the cost of performing one full corruption exposure. Notice that the total amount spent on exposing corrupt politicians will be the sum of the amounts spent on each exposure. The representative voter's expected utility is defined as:

\[
U_V (\psi, \dd, \bups) \ = \ \indf \{\psi=G \}r_G
\]

Where $\indf$ is the indicator function for $\psi=G$ and $r_G$ the value of the public good for the voter. Notice that no $\psi=B$ is observed on the equilibrium path, as underspending is a dominated strategy.

Also, any retention rule selected for the voters is sequentially rational, because there is no uncertainty about the results when they vote. I choose the optimal rule for the voter as dismiss all incumbents when $\psi=B$ or replace incumbents that were successfully exposed by challengers when $\psi=G$. This rule is ex-post efficient as over-dismissal would make incumbents to pocket all the money regardless of $\eta$.

Finally, I solve for the \textit{Perfect Bayesian Equilibrium} \citep{Fudenberg1991book, Fudenberg1991}. A perfect Bayesian equilibrium consists in a pair of strategies and beliefs such that:

\begin{enumerate}
 \item In each information set, the decision should be sequentially rational;
 \item Each strategy is compatible with its beliefs concerning the behavior on and off the equilibrium path.
\end{enumerate}

Also, as this is a signaling game, I use \textit{universal divinity} as the equilibrium selection criteria \citep{BanksSobel1987}.\footnote{The restriction imposed by the universal divinity requires that the challengers, facing a deviation from the equilibrium path, put probability one on the type that are more likely to deviate. Moreover, as we have a continuum of types in one of the types dimensions, we use the approach by \citet{Malaith1987}, which consists in find the monotonicity in the payoffs and single crossing conditions, characterizing the behavior of the types inside the intervals of the type space, analyzing the incentives to pool or separate among the types.}

\begin{definition}
 \label{def_eqn}
 A Perfect Bayesian Equilibrium for the game described, with $|I|=K$ and $|C|=L$, $K$ and $L$ in $\mathbb{N}$, type space $T=[0,A]$, consists in optimal strategies $\bveps^{*}$, $\bvphi^{*}$, $\bups^{*}$ and beliefs $\mu^*$, that satisfy
 \begin{enumerate}
  \item $\forall t_i \in T$, $\varepsilon^{*}_i(t_i)$ maximizes $ U_i (\varepsilon_i; \ t_i, \ \bvphi^{*}, \ \bups^{*}, \ \varepsilon_{-i}^{*}) $ $\forall i \in \{1, \cdots, K\}$.
  \item $\forall \bveps \in \left[0,A \right]^K $ and $\psi \in \{B, \ G \}$, $\bvphi^{*}_j(\bveps, \psi)$ maximizes $ U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}, \ \mu^*) $, $\forall j \in \{1, \cdots, L\}$
  \item $\forall \psi \in \{B, \ G \}$ and $\dd \in \{0,1\}^L$, $\bups^{*}(\psi, \dd)$ maximizes $ U_V (\psi, \dd, \bups^*) $.
  \item The beliefs are derived using Bayes rule whenever possible, and for all $\varepsilon_i$ that are off-the-equilibrium path, $\mu^*(t_i| \varepsilon_i)>0$ (in fact, 1) only if $\widehat{\varepsilon}_i \in \arg \min_{t_i} p(t_i, \widehat{\varepsilon}_i)$, where $ p(t_i, \widehat{\varepsilon}_i)$ is the profit from deviating from $\varepsilon_i$ to $\tilde{\varepsilon}_i$ for a type $t_i$.
 \end{enumerate}
\end{definition}

## Single-Member Districts with One Challenger

Let $|I|=1$ and $|C|=1$. Solving the game backwards, the voters retain the incumbent if the policy result was good and no corruption was exposed.

From the challenger's perspective, as there is no cost of entry, she decides whether to invest her campaign resources in exposing the incumbent. She does so when the expected utility of exposing is greater than or equal the expected utility of not exposing, given her beliefs about the true value of $\eta$. Thus:

\[
B \int_{t_i \in T} \Prob (\bups = (0,1)\ | \ \eta, \varepsilon^*, \varphi)\mu^*(t_i|\varepsilon^*) d\mu - c \varphi(\psi, \varepsilon^*) \geq 0
\]

Rearranging and applying the fact that $ \Prob(\bups = (0,1) | \varepsilon^*, \varphi ( \psi, \varepsilon^*), \eta) = \varphi(\psi, \varepsilon^*) \lambda(\varepsilon^*-\eta) $ and $\mu^*(t_i | \varepsilon^*) = \mu(\eta) = \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta}$,

\[
B \varphi(\psi, \varepsilon^*) \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta - c \varphi(\psi, \varepsilon^*)
\]

Isolating $\varphi(\psi, \varepsilon^*)$, letting $\lambda_\varepsilon = \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta$ and $Q(B, c) = \dfrac{c}{B}$, we see that sequential rationality implies that the challenger expose corrupt incumbents for sure whenever $\lambda_\varepsilon > Q(B, c)$, never expose corruption when $ \lambda_\varepsilon < Q(B, c)$, and is indifferent when $\lambda_\varepsilon = Q(B, c)$.

Now let $\dfrac{\int_0^A \lambda(A - \eta)f(\eta) d\eta}{\int_0^Af(\eta)d\eta} = Q^*$. If $Q \geq Q^*$, we have only one equilibrium, which will be to play $A$ regardless of $\eta$. And there will be no exposures in equilibrium, as they are too expensive to be performed. To avoid this situation, we impose the following condition:

\begin{assumption}\label{assExist}
We assume $B$ and $c$ are restricted in such a way that $Q<Q^*$.
\end{assumption}

Given this assumption, there exists $\overline{\eta}$ such that

\[
\lambda_A = \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta)f(\eta) d\eta}{\int_{\overline{\eta}}^Af(\eta)d\eta} = Q(B, c)
\]

In equilibrium, we seek for roots to the equation $\lambda_A-Q(B, c)$. These roots are well characterized, as if $\overline{\eta}=0$, $\lambda_A - Q (B, c) \geq 0$ and if $\overline{\eta}=0$, $\lambda_A=0$ and so the value is negative. As this function is continuous, by the intermediate value theorem, we have a root, that we call $\overline{\eta}$. The monotonicity of $f$ also ensures that each root is unique.

$\overline{\eta}$ has an intuitive interpretation: it is the minimal value for $\eta$ such that above this value, the incumbent always prefers to play $A$ regardless of $\eta$.

Now, let a probability function $\delta(\varepsilon)$ to characterize the equilibrium amount of negative campaign when $\varepsilon \in [ 0, \ \overline{\eta}]$. The optimal $\varepsilon$ solves the equation $\lambda_\varepsilon = Q(B, c)$, making the challenger indifferent between exposing or not the incumbent's corruption. As $\lambda(.)$ has a well defined inverse function, the optimal strategy for the incumbent is:

\begin{equation*}
\varepsilon^*(\eta) \ = \ \eta + \lambda^{-1}\left(\dfrac{c}{B}\right)
\end{equation*}

Therefore, the required value plus a kickback $\kappa$ defined as $\kappa = \lambda^{-1}\left(\dfrac{c}{B}\right)$, whenever $\eta \in [0, \overline{\eta}]$, and $A$ otherwise.

Now, reasoning backwards, the incumbent only plays this strategy when it is incentive compatible for her, and to be an optimal response, it should be an $\arg \max$ of $U_I$. Taking the derivative of $U_I$ and setting it to zero gives us the following differential equation for $\delta(\varepsilon)$:

\[
\dfrac{d \delta}{d \varepsilon} + \delta(\varepsilon)\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)} = \frac{1}{B}\frac{u^{'}(\kappa)}{\lambda(\kappa)}
\]

Under the boundary condition that $\delta(\kappa)=0$. This represents a well defined first order differential equation, that has an straightforward unique solution determined by the boundary condition. Solving for $\delta(\varepsilon)$, we have:

\[
\delta(\varepsilon) = \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right)
\]

Combining all these results together  us the following lemma.

\begin{lemma}
 \label{lemma_m1}
 A Perfect Bayesian Equilibrium for the game when $|I|=1$ and $|C|=1$ is a pair of strategies and beliefs such that the optimal strategies are
 \begin{enumerate}
  \item For the incumbent
  \[
  \varepsilon^{*}(\eta) \ = \ \twopdo{\eta + \kappa}{\eta \leq \overline{\eta}}{A}
  \]
  \item For the challenger
  \[
  \varphi^*(\varepsilon) \ = \ \threepdo{0}{\varepsilon < \kappa}{\delta(\varepsilon)}{\varepsilon \in [\kappa, \overline{\eta}]}{\delta(A)}
  \]
  \item And for the voter, retain the incumbent if $\dd=0$ and $\psi=G$ and dismiss otherwise.
 \end{enumerate}
 With 
 \[
 \delta(\varepsilon) = \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right)
 \]
 and
 \[
 \kappa = \lambda^{-1}\left(\dfrac{c}{B}\right)
 \]
 And the optimal beliefs updated by Bayes rule whenever possible, with the out-of-the path beliefs restricted by the Universal Divinity Criteria.
\end{lemma}

Let $\varepsilon^*$ and $\varphi^*$ as defined in the Lemma \ref{lemma_m1}. To show the existence and the characteristics of the separating equilibrium, following \citet{Malaith1987} we need to prove the following Claim:

\begin{claimnn}\label{claim1}
The expenditure in weakly increasing in the type $t_i \in T$
\end{claimnn}

\begin{proof}[Proof of Claim \ref{claim1}]
First, notice that the type space $T$ is a compact set, and thus a complete lattice. Then:

\[
\dfrac{\partial^2 U}{\partial \varepsilon \partial \eta} = -u^{''} + B(\varphi(\varepsilon)\lambda^{''} + \varphi^{'}(\varepsilon)\lambda^{'}) 
\]

And so, as $\lambda$ is weakly increasing, $\lambda^{''}>0$ and $u$ is concave, $U$ satisfies the increasing differences properties in $\varepsilon$ and $t$. As $T$ is a lattice, we have that $\varepsilon^{*}(\eta)$, which is a maximum for $U_I(t_i, \varepsilon(t_i) )$, is also weakly increasing in $\eta$.\footnote{See \citet{MilgromShannon1994}, theorem 6.}

@@

As I derived the optimal strategies for the incumbent and challenger's strategies, it remains to show that no type $t_i \in T$ have incentives to deviate. Define the profit that a type $t_i$ gains when she deviates from $\varepsilon(t_i)$ to $\tilde{\varepsilon}$ as:

\[
p(t_i, \varepsilon(t_i), \varphi, \tilde{\varepsilon}) \ = \ u (\varepsilon(t_i) - \eta) + B \left( \varphi(\tilde{\varepsilon})\lambda(\varepsilon(t_i)-\eta) - \varphi(\varepsilon(t_i))\lambda(\varepsilon(t_i)-\eta) \right)
\]

Now consider the following Claim:

\begin{claimnn}\label{claim2}
No type has incentive to deviate from the equilibrium enunciated in Lemma \ref{lemma_m1}.
\end{claimnn}

\begin{proof}[Proof of the Claim \ref{claim2}]

Let $t_i = \eta$. We then have that

\[
\dfrac{\partial p}{\partial \eta} \ = \ \left(\dfrac{\partial \varepsilon}{\partial \eta} - 1 \right) (u^{'}(\varepsilon-\eta) - B\varphi(\varepsilon)\lambda^{'}(\varepsilon-\eta))
 - B \varphi(\tilde{\varepsilon})\lambda^{'}(\varepsilon-\eta)) - \dfrac{\partial \varepsilon}{\partial \eta} B \varphi^{'}(\varepsilon)\lambda(\tilde{\varepsilon}-\eta) - u^{'}(\varepsilon-\eta)
\]

Applying the fact that $\dfrac{\partial}{\partial \varepsilon}\left[ \varphi(\varepsilon) \lambda(\varepsilon - \eta) \right] = \dfrac{u^{'}(\varepsilon(\tilde{\eta})-\eta)}{B}$:

\[
\dfrac{\partial p}{\partial \eta} \ = \ -u^{'}(\varepsilon-\eta) + B(\varphi(\varepsilon)\lambda^{'}(\varepsilon-\eta) - \varphi(\tilde{\varepsilon}) \lambda(\tilde{\varepsilon} - \eta))
\]

And as long as the challenger plays $\varphi^*$, that is increasing on $\varepsilon$, the $ \dfrac{\partial p}{\partial \eta} < 0 $. Thus, $t_i$ has no incentives to deviate from $\varepsilon(\eta)$.

For the voter, the optimal $\bups$ is $\bups=(1,0)$ when $\psi=G$ and $\dd=0$ and $\bups=(0,1)$ otherwise.

The beliefs are derived using Bayes rule:

\[
\mu(\eta | \varepsilon) = \dfrac{f(\eta)}{\int_\kappa^\varepsilon f(\eta) d\eta}
\]

As no discontinuity is present inside the interval $[\kappa, \overline{\eta}]$, the set of players who deviate under these strategies is a measure zero set. So, $(\varepsilon^*, \ \varphi^*, \ \bups^*, \ \mu^* )$, as defined in the Lemma \ref{lemma_m1} are a Perfect Bayesian Equilibrium for the game.

## Single-member District with Many Challengers

Let $|I|=1$ and $|C|=L$. Solving backwards, the optimal strategy for the voters is to retain the incumbent if the public goods were successfully provided and no corruption was successfully uncovered. If the voters dismiss the incumbent, they randomly select a challenger among all challengers.

One might think that an optimal scheme would be to reward the challengers that uncovered the corruption scandal. The problem with this consideration is twofold: first, once the corruption has been detected, all challengers could use these facts in their campaigns, making the corruption exposure a non-excludable public good. Second, even if we consider that challengers inherit the votes from the exposed incumbent, the collective action remains, as every challenger will have incentives for negative campaign, but if all do, the voter will keep choosing by chance. The equilibrium changes slightly but qualitatively, it is still worse than just one challenger.

Challengers observe $\psi$ and $\varepsilon$, and have to simultaneously compute the negative campaign investment $\varphi_i$. As challengers have the same utility function, we solve for a symmetric equilibrium.\footnote{As the payoffs and costs are symmetric here, the symmetric Nash equilibrium is the adequate choice for this problem. If we had heterogeneity on challengers, induced by ideological preferences of the electorate, or other characteristics, the symmetry assumption would not be well suited.}

Let $\lambda(\varepsilon-\eta) = \lambda_\varepsilon$. If we have $k$ players investing in negative campaign against the incument politician, the probability that the incumbent loses the election is:

\[
\Prob(\text{success} | \text{k exp.})  \ = \ 1 - (1-\lambda_\varepsilon)^k
\]

Let $\varphi$ the probability that all players but $i$, invest in negative campaign. Then, the chance of having $k$ players investing in exposing the corrupt incumbent among the $L-1$ players is:

\[
\Prob( \text{k exp.}) \ = \ {L \choose k} \varphi^k (1-\varphi)^{L-1-k}
\]

And the composite probability of losing an election is given by:

\[
f(\varphi, x) = \sum_{k=0}^{L-1} {L \choose k} \varphi^k (1-\varphi)^{L-1-k} \cdot (1 - (1-\lambda_\varepsilon)^{k+x})
\]

And when $i$ invests in negative campaign, we let $x=1$ in $f$. This allows us to compute the expected utility for the challenger $i$ as:
